---
title: "Visualizing Snowdepth"
output:
 html_document:
  code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Government Camp, OR

Located just over an hour East of Portland, Government Camp is a small "alpine" town. The town is the gateway to several ski areas on Mt. Hood: Timberline, Mt. Hood Meadows, Ski Bowl, and Summit. Snow is the lifeblood of this town in the winter. Without it, local businesses wouldn't survive the winters.

Here are some important summary stats for Government Camp:

| Summary Stats |  |
|----|----|
| Elevation | 3,914 ft (1,193 m) |
| Population | 193 |
| Area | 0.75 sq mi (1.94 km2) |

```{r message = FALSE, warning = FALSE}
#install.packages('plotly')
#install.packages('lubridate')
#install.packages('tidyr')
#install.packages('dplyr')

library(plotly)
library(lubridate)
library(tidyr)
library(dplyr)
#loading the packages

source('data/govy-data.R')
#loading the script that pulls the data from NOAA

```
``` {r warning = FALSE}

snow_depth <- govy_data$snwd %>%
  replace_na(list(snwd = 0)) %>%
  mutate(month_char = month(date, label = TRUE, abbr = TRUE)) %>%
  group_by(year = year(date), month = month(date), month_char) %>%
  summarise(avg_depth = mean(snwd))
#group by year and week, summarize as weekly snow depth
#looking for way to display the month abbr instead of number. adding as factor
#adds a bunch of traces for some reason. adding as character, loses order

avg_obs_temp <- govy_data$tobs %>%
  group_by(year = year(date), month = month(date)) %>%
  summarise(avg_obs_temp = mean(tobs))
#this has two fewer rows than tmin and tmax, not working with it at the moment
avg_min_temp <- govy_data$tmin %>%
  group_by(year = year(date), month = month(date)) %>%
  summarise(avg_min_temp = mean(tmin))
avg_max_temp <- govy_data$tmax %>%
  group_by(year = year(date), month = month(date)) %>%
  summarise(avg_max_temp = mean(tmax))

avg_temps <- left_join(avg_min_temp, avg_max_temp, by = c('month', 'year'))
avg_temps$avg <- rowMeans(avg_temps[3:4], na.rm = TRUE)
#temps still seem off. it's in the data I think. Too hot

snow_depth$avg_temp <- avg_temps$avg

snow_plot <- snow_depth %>% plot_ly(
    x = ~year, 
    y = ~avg_depth, 
    color = ~avg_temp, 
    frame = ~paste0(sprintf("%02d", month), " - ", month_char),
    text = ~paste('<i>Date</i>: ', month_char, year,
                  '<br><b>Avg. Depth</b>: ', avg_depth, 
                  '<br><b>Avg. Temp</b>: ', avg_temp),
    hoverinfo = 'text',
    type = 'bar'
  ) %>%
  layout(
    title = "Average Snow Depth by Month", 
    yaxis = list(title = "Average Depth (mm)")
  ) %>%
  animation_opts(
    frame = 1500,
    transition = 750,
    easing = "linear"
  ) %>%
  animation_slider(
    currentvalue = list(prefix = "Month: ")
  )

snow_plot
```
